Fig2: Candidate genes

### 2020-05-03 analysis/figure-2.Rmd
now all have labels

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex,
          treatment != "control") %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~gene, scales = "free_y", nrow = 2) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text.y = element_text(face = "italic"),
          strip.text.x = element_text(face = "italic"),
          axis.text.x = element_blank()) +
    labs(y = paste(whichsex, "gene expression", sep = " "),
         x = NULL) +
    geom_signif(comparisons = list(c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0)

@@

c <- candidateboxplot("hypothalamus", c("DRD1", "HTR2C"), "female") + labs(x = NULL, title = "") 
g <- candidateboxplot("pituitary", c( "AVPR1A", "CRHR1" ), "female") + labs(x = NULL, title = "")
k <- candidateboxplot("gonad", c("ESR1", "PGR"), "female") + labs(x = NULL, title = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

d <- candidateboxplot("hypothalamus",  c("DRD1", "HTR2C"), "male") + labs(x = NULL, title = " ") 
h <- candidateboxplot("pituitary", c("AVPR1A", "CRHR1"), "male") + labs(x = NULL, title = " ")
l <- candidateboxplot("gonad", c("ESR1", "PGR"), "male") + labs(x = NULL, title = " ") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

  p <- candidatevsd %>%
    filter(tissue %in% whichtissue,
          gene %in% whichgenes,
          sex %in% whichsex,
          treatment != "control") %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    ggplot(aes(x = treatment, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_wrap(~gene, scales = "free_y", nrow = 2) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text.y = element_text(face = "italic"),
          strip.text.x = element_text(face = "italic"),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(y = paste(whichsex, "gene expression", sep = " "),
         x = NULL) +
    geom_signif(comparisons = list(c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  
                map_signif_level=TRUE,
                textsize = 1.5, family = 'Helvetica',
                vjust = 1.5, size = 0)

@@

c <- candidateboxplot("hypothalamus", c("DRD1", "HTR2C"), "female") + labs(x = NULL, title = "") 
g <- candidateboxplot("pituitary", c( "AVPR1A", "CRHR1" ), "female") + labs(x = NULL, title = "")
k <- candidateboxplot("gonad", c("ESR1", "PGR"), "female") + labs(x = NULL, title = "")

d <- candidateboxplot("hypothalamus",  c("DRD1", "HTR2C"), "male") + labs(x = NULL, title = " ") 
h <- candidateboxplot("pituitary", c("AVPR1A", "CRHR1"), "male") + labs(x = NULL, title = " ")
l <- candidateboxplot("gonad", c("ESR1", "PGR"), "male") + labs(x = NULL, title = " ")
